Bayesian inference of relative fitness on high-throughput pooled competition assays

### 2023-12-20 doc/_experiment.qmd
Add explanation of uncertainty sources in figure description

![**Typical competitive fitness experiment**. (A) Schematic of the typical
experimental design to determine the competitive fitness of an ensemble of
barcoded genotypes. Genotypes are pooled together and grown over multiple
growth-dilution cycles. At the end of each cycle, a sample is processed to
generate a library for amplicon sequencing. (B) Typical barcode trajectory
dataset. From each time point, the relative frequency of each barcode is
determined from the total number of reads. Shades of blue represent different
relative fitness. Darker gray lines define the typical trajectory of neutral
lineages.](./figs/fig01){#fig-01}

>>>>

![**Typical competitive fitness experiment**. (A) Schematic of the typical
experimental design to determine the competitive fitness of an ensemble of
barcoded genotypes. Genotypes are pooled together and grown over multiple
growth-dilution cycles. At the end of each cycle, a sample is processed to
generate a library for amplicon sequencing. (B) Typical barcode trajectory
dataset. From each time point, the relative frequency of each barcode is
determined from the total number of reads. Shades of blue represent different
relative fitness. Darker gray lines define the typical trajectory of neutral
lineages. 
<span style="color: #912E27;">
(C) Sources of uncertainty accounted for by our method. The Bayesian
model fit to the data propagates uncertainties from the categories schematically
depicted to all parameters in the inference.
</span>](./figs/fig01){#fig-01}
